---
title: "p8105_hw1_os2424"
author: "Ou Sha"
output: github_document
date: "2023-09-23"
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
```

# Problem 1
```{r}
library(moderndive)
data("early_january_weather")
# find names of variables in dataset
?early_january_weather
names(early_january_weather)
# find size of dataset
nrow(early_january_weather)
ncol(early_january_weather)
# find mean temp
mean(early_january_weather$temp)
```
The variables in the dataset are:
origin is weather station;
year, month, day, hour are time of recording;
temp, dewp are temperature and dewpoint in F; 
humid is relative humidity;
wind_dir, wind_speed, wind_gust are wind direction in degrees, spee and gust speed in mph;
precip is precipitation in inches;
pressure is sea level pressure in millibars;
visib is visibility in miles;
time_hour is date and hour of the recording as a POSIXct date; 

The number of rows are 358, and the number of columns are 15.
The mean temperature is 39.58212F.

```{R}
# make scatter plot of temp vs. time_hour
ggplot(early_january_weather, 
       aes(x = time_hour, y = temp, color = humid)) +
  geom_point() +
  labs(title = "scatterplot of temp vs. time_hour",
       x = "date and hour",
       y = "temperature F")
```
There is a pattern that humidity increases as temperature decreases. Temperature raises during daytime and drops during nighttime. 

```{R}
ggsave("P1 Scatter plot.png", plot = last_plot())
```

# Probleam 2
