---
title: "p8105_hw1_os2424"
author: "Ou Sha"
output: github_document
date: "2023-09-23"
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
```

# Problem 1
```{r}
library(moderndive)
data("early_january_weather")
# find names of variables in dataset
?early_january_weather
names(early_january_weather)
# find size of dataset
nrow(early_january_weather)
ncol(early_january_weather)
# find mean temp
mean(early_january_weather$temp)
```
There are 15 variables:\
1. origin: weather station;\
2. year, month, day, hour: time of recording;\
3. temp, dewp: temperature and dewpoint in F;\
4. humid: relative humidity;\
5. wind_dir, wind_speed, wind_gust: wind direction in degrees, spee and gust speed in mph;\
6. precip: precipitation in inches;\
7. pressure: sea level pressure in millibars;\
8. visib: visibility in miles;\
9. time_hour: date and hour of the recording as a POSIXct date;\

The number of rows are 358, and the number of columns are 15.\
The mean temperature is 39.58212F.

```{r}
# make scatter plot of temp vs. time_hour
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point() + labs(title = "scatterplot of temperature vs. time_hour",
                      x = "date and hour", y = "temperature F")
```

Patterns that are apparent in this plot:\
Humidity tends to increase as temperature decreases. Temperature rises during the daytime and drops at night.

```{r}
ggsave("P1 Scatter plot.png", plot = last_plot())
```

# Probleam 2
```{r}
# create a data frame
set.seed(5)
random_sample <- rnorm(10)
df <- tibble(vec_random = random_sample, 
       vec_logical = random_sample > 0,
       vec_character = letters[1:10],
       vec_factor = factor(sample(c(1, 2, 3), size = 10, replace = TRUE)))
df
```

```{r}
# take mean of random sample
mean(pull(df, vec_random))
# take mean of logical vector
mean(pull(df, vec_logical))
# take mean of character vector
mean(pull(df, vec_character))
# take mean of factor vector
mean(pull(df, vec_factor))
```
Means can be calculated for random samples and logical vectors, but not for character vectors and factor vectors.

```{r, eval=FALSE}
# apply as.numeric function to logical, character, and factor variables
num_logic = as.numeric(pull(df, vec_logical))
num_character = as.numeric(pull(df, vec_character))
num_factor = as.numeric(pull(df, vec_factor))
```
Using `as.numeric` function change the type of certain variable to numeric variables. For logical variables, True turns to 1 and False turns to 0. For character variables, if the variables are not numbers (e.g. letters), they cannot be converted to numeric variables and there will be a warning when `as.numeric` applied. If the variables are numbers, (e.g. "1","2"), they can be converted to numeric variables. For factor variables, they can be converted to numeric variables corresponding to the order of the level.\
This helps to explain why warning messages arise when `as.numeric` is not used before applying the mean() function to calculate the mean of a character or factor vector.
